---
title: "Raman Data Processing"
subtitle: "Data from Pikes Peak and Mt. Evans"
author: "Rachel Havranek"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output: 
  html_document:
    toc: yes
---
# Loading libraries & data, and adding some metadata
```{r setup, echo = FALSE, message=FALSE, warning=FALSE}
# load libraries
library(tidyverse)
library(latex2exp)
library(plotly)
source(file.path("scripts", "Custom_functions.R"))

# global knitting options for automatic saving of all plots as .png and .pdf
knitr::opts_chunk$set(
  dev = c("png", "pdf"), fig.keep = "all",
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.path = file.path("fig_output", paste0(gsub("\\.[Rr]md", "", knitr::current_input()), "_"))
)
```

```{r load all data}
pikes_data <- read_csv("data/PP_raman_data.csv")
evans_data <- read_csv("data/ME_Raman Data.csv")
Nasdala_idealized_line <- read_csv("data/Nasdala.csv")
```

Modify the sample names for ease of reading, where PP stands for Pikes Peak, ME stands for Mt. Evans. Samples are numbered from 1 - 6 with the lowest elevation sample being 1 and highest elevation sample being. 
```{r modify sample names}
pikes_data <- pikes_data %>% 
    mutate (
      Peak = "Pikes Peak",
      papername = 
        ifelse(Sample_Name == "PP2084", "PP1", #If True, add label PP2
          ifelse( Sample_Name == "PP2479", "PP2", #If True, add label PP2
            ifelse (Sample_Name == "PP2907", "PP3", #If true, add label PP3
              ifelse (Sample_Name == "PP3597", "PP4", #If true, add label PP4
                ifelse (Sample_Name == "PP3971", "PP5", "PP6")     #if true, add label PP5, ELSE add the label PP6
                    )      
                  )
                )
              )
    )

evans_data <- evans_data %>% mutate(
  Peak = "Mount Evans",
  papername = ifelse (Sample_Name == "ME10", "ME1_2872",
                ifelse (Sample_Name == "ME8", "ME2_3596", 
                  ifelse (Sample_Name == "ME3", "ME3_3978",  
                          "ME4_4345")
                )
              )
            )
```

# Some very light statistics
This chunk uses the raman_summary function that can be found in the scripts folder in the "Custom Functions.R" file 
```{r}
pikes_flatlist <- pikes_data %>% 
  group_by(papername, grain) %>% 
  raman_summary()
view(pikes_flatlist)

evans_flatlist <- evans_data %>% 
  group_by(papername, grain) %>% 
  raman_summary()

view(evans_flatlist)
```

# Main text figures
```{r figure 2}
#Figure 2a
evans_violin <- evans_data %>% 
  filter(papername != "NA") %>% 
  ggplot()+
    geom_violin(aes(papername, FWHM, fill = Sample_Name), scale = "count", na.rm = TRUE, draw_quantiles = c(0.25, 0.5, 0.75))+
    scale_fill_manual(values = c("#FDE0A1", "#782281", "#EA5661"))+
    scale_y_continuous(expand = c(0,0), limits = c(0,36))+
    ylab(TeX('$\\FWHM (cm^{-1})')) +
    theme_classic()+
    theme(
      panel.border=element_rect(fill=NA,size = 1),
      text = element_text(size = 12),
      legend.position = "none", 
      axis.ticks = element_line(color="black"),
      axis.line = element_line(color = NA),
      axis.text.y = element_text(color = "black", size = 12),
      axis.text.x = element_text (color = "black", size = 12),
      axis.title.x = element_blank()
    )

print(evans_violin)

#Figure 2b
evans_grain_summary <- evans_flatlist %>% filter(papername != "NA") %>% 
  ggplot()+
  geom_point(aes(FWHM_median, FWHM_sd, fill = papername), pch=24, size=4)+
  scale_fill_manual(values = c("#782281", "#EA5661", "#FDE0A1"))+
  scale_x_continuous(expand = c(0,0), limits = c(0,36))+
  scale_y_continuous(expand = c(0,0), limits = c(0,12))+
    xlab(TeX("median value of of FWHM $\\(cm^{-1})$"))+
    ylab(TeX("standard deviation of FWHM $\\(cm^{-1})$")) +
    theme_classic()+
    theme(
      panel.border=element_rect(fill=NA,size = 1),
      text = element_text(size = 12),
      legend.position = "none", 
      axis.ticks = element_line(color="black"),
      axis.line = element_line(color = NA),
      axis.text.y = element_text(color = "black", size = 12),
      axis.text.x = element_text (color = "black", size = 12),
      axis.title.x = element_blank()
    )
evans_grain_summary

#Figure 2c
pikes_violin <- pikes_data %>% 
  ggplot()+
    geom_violin(aes(papername, FWHM, fill = papername), scale = "count", draw_quantiles = c(0.25, 0.5, 0.75))+
    scale_fill_manual(values = c("#000004", "#7D2482", "#FD9A6A"))+
    scale_y_continuous(expand = c(0,0), limits = c(0,36))+
    ylab(TeX('$\\FWHM (cm^{-1})')) +
    theme_classic()+
    theme(
      panel.border=element_rect(fill=NA,size = 1),
      text = element_text(size = 12),
      legend.position = "none", 
      axis.ticks = element_line(color="black"),
      axis.line = element_line(color = NA),
      axis.text.y = element_text(color = "black", size = 12),
      axis.text.x = element_text (color = "black", size = 12),
      axis.title.x = element_blank()
    )
print(pikes_violin)

#Figure 2d
pikes_grain_summary <- pikes_flatlist %>% filter(papername != "NA") %>% 
  ggplot()+
  geom_point(aes(FWHM_median, FWHM_sd, fill = papername), pch=22, size=4)+
  scale_fill_manual(values = c("#000004", "#7D2482", "#FD9A6A"))+scale_x_continuous(expand = c(0,0), limits = c(0,36))+
  scale_y_continuous(expand = c(0,0), limits = c(0,12))+
    xlab(TeX("median value of of FWHM $\\(cm^{-1})$"))+
    ylab(TeX("standard deviation of FWHM $\\(cm^{-1})$")) +
    theme_classic()+
    theme(
      panel.border=element_rect(fill=NA,size = 1),
      text = element_text(size = 12),
      legend.position = "none", 
      axis.ticks = element_line(color="black"),
      axis.line = element_line(color = NA),
      axis.text.y = element_text(color = "black", size = 12),
      axis.text.x = element_text (color = "black", size = 12),
      axis.title.x = element_blank()
    )
pikes_grain_summary
```

# Supplementary text figures

#### Figure S3
```{r figure S3, echo = FALSE}
evans_bygrain_subplot1 <- evans_data %>% 
  filter (papername == "ME1_2872") %>% 
  filter (grain=="Z01" | grain== "Z02" | grain== "Z03" | grain=="Z04" | grain=="Z05" | grain== "Z06" | grain== "Z07" | grain=="Z08")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME1")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))

evans_bygrain_subplot2 <- evans_data %>% 
  filter (papername == "ME1_2872") %>% 
  filter (grain=="Z09" | grain=="Z10" | grain=="Z11" | grain=="Z12" | grain=="Z13" |grain=="z14"| grain=="z15"| grain=="z16" | grain=="z17")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME1")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))

evans_bygrain_subplot3 <- evans_data %>% 
  filter (papername == "ME1_2872") %>% 
  filter (grain=="z21"|grain=="z22"|grain=="z23"|grain=="z24"|grain=="z26"|grain=="z27"|grain=="z28"|grain=="z30"|grain=="z32")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME1")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))


evans_bygrain_subplot4 <- evans_data %>% 
  filter (papername == "ME2_3596") %>% 
  filter (grain=="Z01" | grain== "Z12" | grain== "Z13" | grain=="Z14" | grain=="Z15" | grain== "Z16" | grain== "Z17")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME2")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))

evans_bygrain_subplot5 <- evans_data %>% 
  filter (papername == "ME2_3596") %>% 
  filter (grain=="Z18"| grain=="Z19"| grain=="Z20" | grain=="Z21" | grain=="Z22" | grain== "Z23" | grain== "Z24")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME2")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))

evans_bygrain_subplot6 <- evans_data %>% 
  filter (papername == "ME2_3596") %>% 
  filter (grain=="Z25" | grain=="Z26" | grain== "Z27" | grain== "Z28" | grain=="Z29"| grain=="Z3"| grain=="Z4" | grain=="Z8")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME2")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))

evans_bygrain_subplot7 <- evans_data %>% 
  filter (papername == "ME4_4345") %>% 
  filter (grain=="Z4" | grain== "Z5" | grain== "Z6" | grain=="Z7" | grain=="8"| grain=="9" | grain=="Z10")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME4")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))

evans_bygrain_subplot8 <- evans_data %>% 
  filter (papername == "ME4_4345") %>% 
  filter (grain== "Z12" | grain== "Z13" | grain=="Z16" | grain=="Z19" |  grain== "Z21" | grain== "Z22")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME4")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))

evans_bygrain_subplot9 <- evans_data %>% 
  filter (papername == "ME4_4345") %>% 
  filter (grain=="Z23"| grain=="Z24" | grain=="Z29" | grain== "Z30" | grain=="Z31" | grain=="Z32")%>% 
          raman_bygrain_figure()+ 
          labs(title = "ME4")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))

evans_bygrain_subplot1
evans_bygrain_subplot2
evans_bygrain_subplot3
evans_bygrain_subplot4
evans_bygrain_subplot5
evans_bygrain_subplot6
evans_bygrain_subplot7
evans_bygrain_subplot8
evans_bygrain_subplot9

```


#### Figure S4 
```{r figure S4}
pikes_bygrain_subplot1 <- pikes_data %>% 
  filter (papername == "PP1") %>% 
  filter (grain <= 22)%>% 
          raman_bygrain_figure()+ 
          labs(title = "PP1")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))
            
pikes_bygrain_subplot2 <- pikes_data %>% 
  filter (papername == "PP1") %>%
  filter (grain > 22 & grain <=31) %>% 
        raman_bygrain_figure()+
          labs(title = "PP1")+
          theme_figure()+
          guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
           color="legend", 
           legend.position="bottom",
           fill=guide_legend(ncol=2))
    

pikes_bygrain_subplot3 <- pikes_data %>% 
  filter (papername == "PP1") %>% 
  filter (grain > 31) %>%
    raman_bygrain_figure()+ 
    labs(title = "PP1")+
    theme_figure()+
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
            color="legend", 
            legend.position="bottom",
            fill=guide_legend(ncol=2))
        
pikesbygrain_subplot4 <- pikes_data %>% 
  filter (papername == "PP3") %>% 
  filter( grain <= 24) %>% 
    raman_bygrain_figure()+
    labs(title = "PP3")+
    theme_figure()+
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
            color="legend", 
            legend.position="bottom",
            fill=guide_legend(ncol=2))

pikesbygrain_subplot5 <- pikes_data %>% 
  filter (papername == "PP3") %>% 
  filter( grain > 24) %>% 
    raman_bygrain_figure()+ 
    labs(title = "PP3")+
    theme_figure()+
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
            color="legend", 
            legend.position="bottom",
            fill=guide_legend(ncol=2))

pikesbygrain_subplot6 <- pikes_data %>% 
  filter (papername == "PP5") %>% 
  filter( grain <= 14) %>% 
    raman_bygrain_figure()+
    labs(title = "PP5")+
    theme_figure()+
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
            color="legend", 
            legend.position="bottom",
            fill=guide_legend(ncol=2))

pikesbygrain_subplot7 <- pikes_data %>% 
  filter (papername == "PP5") %>% 
  filter( grain > 14) %>% 
    raman_bygrain_figure()+
    labs(title = "PP5")+
    theme_figure()+
    guides(linetype = guide_legend(label.hjust = 0, label.vjust = 0.5, keyheight = 2),
            color="legend", 
            legend.position="bottom",
            fill=guide_legend(ncol=2))

pikes_bygrain_subplot1
pikes_bygrain_subplot2
pikes_bygrain_subplot3
pikesbygrain_subplot4
pikesbygrain_subplot5
pikesbygrain_subplot6
pikesbygrain_subplot7
```


## Other figures 

